Data Specialization for a Staged Lambda Calculus

### 2014-11-08 paper/splitting.tex
cleaning up latex warnings

The splitting algorithm for stage~\bbone\ terms, as specified by the
judgment $e \splitonesym [c,l.r]$ in \cref{fig:termSplitOne}, proceeds
recursively on the structure of~$e$.
When $e$ is a terminal (a variable or base constant)
splitting yields a combined term formed by tupling $e$ with a \texttt{()} precomputation, and the trivial resumer \texttt{()}. (Stage~\bbone\ terminals, by definition, contain no stage~\bbtwo\ subcomputations.)  For example, the integer constant \texttt{3} splits into the combined term \texttt{(3,())} and resumer \texttt{\_=>()}.

@@

As with stage~\bbone\ terms, the splitting algorithm for stage~\bbtwo\ terms,
as specified by the judgment $e \splittwosym [p,l.r]$ in \cref{fig:termSplitTwo}, is defined on the local structure of $e$.
In the terminal cases of
constants and variables, splitting generates trivial precomputations that are \texttt{()}, and resumers consisting of the original term.
For example, the integer constant \texttt{3} splits into the
precomputation \texttt{()} and resumer \texttt{\_=>3}.

>>>>

The splitting algorithm for stage~\bbone\ terms, as specified by the
judgment $e \splitonesym [c,l.r]$ in \cref{fig:termSplit}, proceeds
recursively on the structure of~$e$.
When $e$ is a terminal (a variable or base constant)
splitting yields a combined term formed by tupling $e$ with a \texttt{()} precomputation, and the trivial resumer \texttt{()}. (Stage~\bbone\ terminals, by definition, contain no stage~\bbtwo\ subcomputations.)  For example, the integer constant \texttt{3} splits into the combined term \texttt{(3,())} and resumer \texttt{\_=>()}.

@@

As with stage~\bbone\ terms, the splitting algorithm for stage~\bbtwo\ terms,
as specified by the judgment $e \splittwosym [p,l.r]$ in \cref{fig:termSplit}, is defined on the local structure of $e$.
In the terminal cases of
constants and variables, splitting generates trivial precomputations that are \texttt{()}, and resumers consisting of the original term.
For example, the integer constant \texttt{3} splits into the
precomputation \texttt{()} and resumer \texttt{\_=>3}.
